---
title: "P8131 HW9"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(flexsurv)
library(survival)
library(MASS)
library(survminer)
library(KMsurv)
library(tidyverse)
```

# 3. Tongue data

Data Description:

* `type`: Tumor DNA profile (1=Aneuploid Tumor, 2=Diploid Tumor)

* `time`: Time to death or on-study time, weeks

* `delta` Death indicator (0: censored/alive, 1: observed/dead)

```{r input}
data(tongue)
tongue <- tongue %>%
  mutate(type = ifelse(type == 1, "aneuploidy", "diploid"))
Surv(tongue$time,tongue$delta,type='right') # 0: censored, 1: observed
```

For each tumor type (aneuploidy and diploid), plot the Kaplan-Meier curve of survival function and its pointwise 95% confidence intervals (using the log transformation). 

```{r}
#survdiff(Surv(time,cens)~treat, data=gehan) # log rank test
survival.fit <- survfit(Surv(time,delta)~type, data = tongue, conf.type='log')
ggsurvplot(survival.fit, conf.int=TRUE)
```
The estimated 1-year survival rate and 95% CI:

```{r}
summary(survival.fit,time=c(365/7))
```

The estimated 1-year survival rate for patients with aneuploid tumor is about $0.654$, with 95% CI $[0.537, 0.797]$,
and the estimated 1-year survival rate for patients with diploid tumor is about $0.4864$, with 95% CI $[0.3302, 0.7164]$.

